\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-22 manuscript.Rnw
Remove extra comma in code
Add sessionInfo() to facilitate replication
Update R packages to newest versions

# Fit models
fit_pfs_wei <- flexsurv::flexsurvreg(
  Surv(pfs_time, pfs_status) ~ female + new1 + new2,
  data = onc_pfs_os,,
  dist = "weibull")

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
summary(ce_sim_psm, labels = labs_cohort) %>%
  format()
@

@@

<<cdtstm_icer>>=
ce_sim_cdtstm <- cdtstm$summarize()
summary(ce_sim_cdtstm, labels = labs_cohort) %>%
  format()
@

@@

>>>>

# Fit models
fit_pfs_wei <- flexsurv::flexsurvreg(
  Surv(pfs_time, pfs_status) ~ female + new1 + new2,
  data = onc_pfs_os,
  dist = "weibull")

@@

<<psm_summary>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
summary(ce_sim_psm, labels = labs_cohort) %>%
  format()
@

@@

<<cdtstm_summary>>=
ce_sim_cdtstm <- cdtstm$summarize()
summary(ce_sim_cdtstm, labels = labs_cohort) %>%
  format()
@

@@

%% -- Session info -------------------------------------------------------------
<<sessionInfo, include=FALSE>>=
sessionInfo()
@
